\documentclass[14pt]{article}

\usepackage{extsizes}

% reformat page size and margin
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
}

%opening
\title{Senior Design Elevator Pitch}
\author{Alan Trester, Sadie Gladden, Zuguang Liu}

\begin{document}

\maketitle

Hello, my name is (Alan/Sadie/Liu) and I would like to talk to you about the project we are working on. It is an automated home garden system for your house. It auto-manages your garden environment by water, soil, sunlight, temperature, and air, whether it being indoor or outdoor. It saves your water, money, and time, and you don't have to worry about it when you are busy or on vacation. The system is modular so it is customizable to your plants' needs. If you don't have a garden and don't know what to grow, the system will give recommendations suitable to your environment. You will also be able to see and manage the environment yourself with the controller that it comes with. Depending on the budget and timeline, we also want to bring in other features such as integration with smart home devices. If you are interested in using or funding our project, let us know by phone number or email.

Alan's Revision:

Hello, my name is (Alan/Sadie/Liu) and I would like to talk to you about our senior capstone project. We are developing an automated garden monitoring system that provides both real-time and historical information about water, sunlight, air temperature, and other environmental conditions. The base system will let you monitor your garden and let you make informed decisions on what plants will benefit most from being planted there. A modular design will allow more features to be added such as an automatic watering system that uses weather predictions to conserve water. To tie it all together, a well designed user experience will allow even the most casual users to be able to access information and configure their garden with ease. We believe that a system like this has plenty of commercial applications for homeowners, hobbyist gardeners, and even farmers. We are open to proposals of any sort, so please do not hesitate to contact us if you'd like to talk more about this project.


\end{document}
