\chapter{Team Description}

\section{Team Members}
	%The group includes three students: \textbf{Alan Trester}, \textbf{Sadie Gladden}, and \textbf{Zuguang Liu}. \\
	
	\textbf{Alan Trester} is an Electrical Engineering student with co-op experience in software, hardware, and manufacturing engineering roles through GE Aviation Systems. He has a strong passion for technology, design, and "making". After graduating he will be pursuing full-time positions in embedded systems or other design engineering roles in the consumer-products industry.\\
	
	\textbf{Eric Krenz} is a Computer Engineering student whose past co-op experience was in hardware, software development, and cybersecurity. He has a passion for engineering, technology, and making the world a better place. Post graduation he will pursue a full-time career in Information Technology Consulting. \\
	
	\textbf{Sadie Gladden } is a Computer Engineering student with co-op experience in software developement, user interface creation, game engine developement, computer graphics, and cloud solutions through Siemens PLM and Siemens Healthcare GmbH. She enjoys exploring the relationship between hardware and software and exploring the connection and overlap of technology and medicine.\\
	
	\textbf{Zuguang Liu} is an Electrical Engineering student who has past Co-op experience in industrical system design, embedded system hardware design, and simple machine learning implementation. After finishing a Bachelor's Degree with a Embedded System minor, he continues to pursue a Master's Degree in Electrical Engineering. 
	
\section{Technical Advisors} 
	
	\textbf{Dr. Zachariah Fuchs} (\href{fuchsze@ucmail.uc.edu}{fuchsze@ucmail.uc.edu}) is the professor for Introduction to Mechatronics. He has extensive knowledge on embedded system design, sensor fusion, robotics and control systems. We believe he could advise us on the overall system architecture as well as specific conponents in the system. \\
	
	%Graying this out for now until we actually talk to Dr Purdy	
	%\textbf{Dr. Carla Purdy} (\href{purdyc@ucmail.uc.edu}{purdyc@ucmail.uc.edu}) is the professor for Embedded Systems with extensive experience in Microcontroller and Microprocessor Design. She is also the advisor for the Embedded Systems Minor. Her expertise will help us justify the project related to Embedded Systems, in order to fulfill the minor requirement for Alan and Liu. \\

	
