\documentclass[]{article}

%opening
\title{Senior Design Team Formation Report}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=20mm,
	top=20mm,
}

\begin{document}

\maketitle

This is a report on the discussion of Senior Design (Capstone) Project for the class of 2021. The group includes three students: \textbf{Alan Trester} (Electrical Engineering), \textbf{Sadie Gladden} (Computer Engineering), and \textbf{Zuguang Liu} (Electrical Engineering).

\section{Project Concept}
An automatic garden monitoring and care system that utilizes a wireless modular design in order to fit a variety of use cases and scenarios. The system will be able to provide detailed information about garden vital statistics and use this information to automatically care for the plants.
\section{Assigned Tasks}
A brief breakdown of the tasks are drafted below.
\begin{itemize}

	\item Firmware Development \& System Architect - Alan Trester
	\begin{itemize}
		\item Design and implement system architecture 
		\item Research methods of communication protocols 
		\item Implement methods for specific features
	\end{itemize}

	\item Frontend Development - Sadie Gladden
	\begin{itemize}
		\item Application creation
		\item UX/UI design and devolopement 
		\item Ensure ease of access to system information and functionality
		\item Assisting in firmware design
	\end{itemize}

	\item Hardware Specification - Zuguang Liu
	\begin{itemize}
		\item Research on the specific hardware used to implement functionalities
		\item Draft a Bill of Material on the hardware
		\item Design circuit and circuit boards to complete the implementation
	\end{itemize}

\end{itemize}

\section{Advisors}
We have asked \textbf{Dr. Zachariah Fuchs} (fuchsze@ucmail.uc.edu) regarding the project advising as well as \textbf{Dr. Carla Purdy} (purdyc@ucmail.uc.edu) regarding the fulfillment for embedded system minor. Confirmation from the advisors are pending.

\section{Meeting Times}
We anticipate to have 6-8 hours of meeting per week. Specific meeting time is to be discussed. 


\end{document}
